### 2015-02-19 proofs.tex
more dunkl operators

We consider $s_{0a}$ for $2 \le a$. We see that $s_{01}$ sends $x_a$ to $-x_a$ and $x_i$ for $i \ne a$ to $x_a-x_1$. We see that $s_{0a}f_1=-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)$. %todo

@@

Let $I$ be the ideal generated by $f_1,\dots, f_{n-1}$. We will show that $A/I$, where $A=k[x_1,\dots,x_{n-1}]$, is a complete intersection by showing that $f_1(x) = \dots = f_{n-1}(x)=0$ implies $x=0$.

>>>>

We consider $s_{0a}$ for $2 \le a$. We see that $s_{0a}$ sends $x_a$ to $-x_a$ and $x_i$ for $i \ne a$ to $x_a-x_1$. We see that:

\begin{align*}
s_{0a}f_1&=s_{0a}\left(-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)\right)\\
&=s_{0a}\left(-x_1^3+c \left(\sum_{i \ne a} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i \ne a} \sum_{j \ne a} x_ix_jx_1\right)+cx_1x_a(x_1-x_i)+c^2x_a^2x_1+2c^2 \sum_{i \ne a} x_ix_ax_1 \right)\\
&=-(x_1-x_a)^3+c \left(\sum_{i \ne a} (x_1-x_a)(x_i-x_a)(x_1-x_a-x_i+x_a)\right)+\\&c^2 \left(\sum_{i \ne a} \sum_{j \ne a} (x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+c(x_1-x_a)(-x_a)(x_1-x_a-x_i+x_a)+c^2(-x_a)^2(x_1-x_a)+\\&2c^2 \sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a) \\
&=-x_1^3+x_a^3+c \left(\sum_{i \ne a} (x_1-x_a)(x_i-x_a)(x_1-x_i)\right)+\\&c^2 \left(\sum_{i \ne a} \sum_{j \ne a} (x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+c(x_1-x_a)(-x_a)(x_1-x_i)+c^2x_a^2(x_1-x_a)+\\&2c^2 \sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a) \\
\end{align*} %todo

@@

We note that the $f_i$ are linearly independent, since $x_i^3$ has nonzero coefficient in $f_j$ only when $i=j$. We will show that $A/I$, where $A=k[x_1,\dots,x_{n-1}]$, is a complete intersection by showing that $f_1(x) = \dots = f_{n-1}(x)=0$ implies $x=0$.
